A pipeline to analyse time-course gene expression data

### 2020-06-24 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\textbf{EAP}: I don't know that describing normalization as part of our tutorial makes sense.
I've tried to change the text.

The manuscript was last compile on 2020-06-24 08:14:28.

\hypertarget{todo-list}{%
\section{TODO list}\label{todo-list}}

\begin{itemize}
\tightlist
\item
  Make clear that it applies to RNASeq and how to call the different functions
  to RNASeq
\item
  Check that clustering can deal with count data.
\item
  Make sure package is compatible bioconductor
\end{itemize}

@@

\textbf{EAP}: Why is this list not the same as the (hidden via echo=FALSE) list at
the beginning of the document? I also needed to install \texttt{BiocWorkflowTools},
\texttt{KEGGprofile} to run the .Rmd

@@

The first steps of analysis of gene expression data is always to do
normalization and quality control checks of the data. However, in what follows, we do not show the steps for normalization, as these are specific to the platform (microarray); the code for the normalization can be found in as a supplemental file \citep{abrams:protocol, park:evalution}.

>>>>

The manuscript was last compile on 2020-06-24 09:03:07.

@@

\textbf{EAP}: Why is this list not the same as the (hidden via echo=FALSE) list at
the beginning of the document? I also needed to install \texttt{BiocWorkflowTools},
\texttt{KEGGprofile} to run the .Rmd
\textbf{NV}: I think some of the libraries above are not needed anymore. Some are
also only used in hidden elements. I just checked that the whole pipeline
works, by executing all command lines the reader will see, and the libraries
are all loaded fine. I think BiocWorkflowTools is only need in the compilation
of the Rmd file.

@@

The first steps of analysis of gene expression data is always to do
normalization and quality control checks of the data. However, in what
follows, we do not show the steps for normalization, as these are specific to
the platform (microarray); the code for the normalization can be found in as a
supplemental file \citep{abrams:protocol, park:evaluation}.
